Simulating High-Dimensional Multivariate Data

### 2021-03-01 letter_bigsimr_CSDA.Rmd
fix double ending to letter

---
institution:
  name: "University of Nevada, Reno"
  department: "Mathematics and Statistics"
  address:
    line1: "1664 N. Virginia Street / 0084"
    line2: "Reno, Nevada 89557"
  phone: "(775) 784-6773"
  fax: "(775) 784-6378"
  url: https://www.unr.edu/math/
  logo: "logos/blue.png"
author:
  first: "Alfred"
  last: "Schissler"
  short: "Grant"
  title: "Ph.D."
  position: "Assistant Professor, Statistics"
  signature: "signature.jpg"
to:
  first: "Alexander"
  last: "Knudson"
  short: "Alex"
date: "`r format(Sys.Date(), format='%d %B %Y')`"
opening: "Dear CSDA Annals of Statistical Data Science Editor(s):"
closing: "Sincerely,"
output:
  pdf_document:
    template: templateSingleSignature.tex
---

@@

Best regards,

>>>>

---
institution:
  name: "University of Nevada, Reno"
  department: "Mathematics and Statistics"
  address:
    line1: "1664 N. Virginia Street / 0084"
    line2: "Reno, Nevada 89557"
  phone: "(775) 784-6773"
  fax: "(775) 784-6378"
  url: https://www.unr.edu/math/
  logo: "logos/blue.png"
author:
  first: "Alfred"
  last: "Schissler"
  short: "Grant"
  title: "Ph.D."
  position: "Assistant Professor, Statistics"
  signature: "signature.jpg"
to:
  first: "Alexander"
  last: "Knudson"
  short: "Alex"
date: "`r format(Sys.Date(), format='%d %B %Y')`"
opening: "Dear CSDA Annals of Statistical Data Science Editor(s):"
closing: "Best regards,"
output:
  pdf_document:
    template: templateSingleSignature.tex
---

@@
